Openness and computational reproducibility in plant pathology: where do we stand and a way forward

### 2022-07-08 analysis/paper/paper.Rmd
Revise this sentence for clarity as per reviewer 2

Recently, open science has been highlighted with many funding agencies expecting data to be available upon the conclusion of the research project [@government_of_canada_2016; @vannoorden2017; @ARC2018], journals in the field promoting the sharing of data [@DelPonte2020], and other scientists interested in sharing and collaborating more widely [@Wald2010].

>>>>

Open science and reproducibility is becoming more mainstream with many funding agencies expecting data to be available upon the conclusion of the research project [@government_of_canada_2016; @vannoorden2017; @ARC2018], journals in the field promoting the sharing of data [@DelPonte2020], and other scientists becoming interested in sharing their raw data and even lab notebook contents [@Wald2010].
